---
title: "Effect of flicker LMS splatter on Adapt JNDs"
---
```{r setup}
library(tidyverse)
library(here)
source(here('R','clean_data.R'))
source(here('R','analyze_results.R'))
source(here('R','normalize_JNDs.R'))
source(here('R','results.plot.R'))
```
# Load in data
This dataset of thresholds in the Steady Adaptation experiment contains the columns:
`participant`,`session`,`axis`,`level`: meta info for each acquisition
`contrastNominalQuick`,`contrastNominalFit`: two slightly different versions the nominal contrast at threshold
`LMSBackgroundNominal`: nominal LMS content of the background spectrum
`JNDNominalQuick`,`JNDNominalFit`: JNDs corresponding to the nominal contrasts
`contrastMeasuredQuick`,`JNDMeasuredQuick`: measured contrast, JND, at threshold
`LMSBackgroundMeasured`: measured LMS content of the background spectrum
`JNDMeasuredQuick`: JND corresponding to the measured quick contrast and background
`ratioContrastMeasuredNominal`: ratio between nominal contrast, and measured contrast
`LMMeasured`: measured L-M contrast of the flicker on the background.
```{r load}
thresholds_splatter <- read_csv(here('data','experimental','adapt.thresholds.splatter.csv'))
```
# Cleaning
For the current analysis, need to group by the acquisition metadata, and need the nominal LMS contrast (`contrastNominalQuick` and `contrastNominalFit`) and the measured LMS contrast of the flicker stimulus (`contrastMeasuredQuick`). Also need the `LMSBackgroundNominal` to convert to JNDs. We also want to rename the participants.
```{r clean}
thresholds_splatter <- thresholds_splatter %>%
  rename_participants() %>%
  group_by(participant, session, axis, level) %>%
  mutate(contrastNominal = contrastNominalFit)
```

# Plot the flicker LMS splatter
```{r visualize flicker LMS splatter}
ggplot(data = thresholds_splatter) +
  # Setup mapping: melanopic level on horizontal, LMS content on vertical
  aes(x = level, y = contrastMeasuredQuick) +
  # Separate panels for participants
  facet_grid(~ participant) +
  
  # Plot each session
  geom_line(aes(group = session), alpha = .6) +
  # Plot median for participant
  stat_summary(fun.y = median, geom = "point", aes(group=1), size =1) +
  stat_summary(fun.y = median, geom = "line", aes(group=1), size =1) +
  stat_summary(fun.y = median, fun.ymax = median_plus_sem, fun.ymin = median_minus_sem,
               geom = "linerange", aes(group = 1), size =1) +  
  
  # Labeling
  ylab("Measured flicker LMS contrast") +
  xlab("Melanopic condition") +
  ggtitle("LMS splatter of flicker") +
  theme_bw()
```
# Predict JNDs

```{r}
threshold_contrasts <- thresholds_splatter %>%
  select(contrastNominal, contrastNominalQuick, contrastMeasuredQuick, LMSBackgroundNominal)
```
 Calculate the ratio between the measured LMS content of the flicker stimulus at threshold (the `contrastMeasuredQuick`), and the nominal content of that stimulus (the `contrastNominalQuick`), for each acquisition.
```{r calculate ratio of measured to nominal flicker}
threshold_contrasts <- threshold_contrasts %>% 
    # Calculate ratio
    mutate(ratioContrastMeasuredNominal = contrastMeasuredQuick / contrastNominalQuick) %>%
    select(-contrastMeasuredQuick, -contrastNominalQuick)
```
Pivot dataframe to wide-format: separate columns for `high` and `low` nominal contrast at threshold per session. Set `high` nominal contrast at threshold equal to `low` nominal contrast at threshold. Pivot back to tall-format, with separate rows for low and high melanopic conditions indicated by columns `level` and `contrastNominal` for the predicted nominal contrast.
```{r equate nominal contrasts}
threshold_contrasts <- threshold_contrasts %>%
    # Pivot to wide-format: separate columns for high/low
    pivot_wider(names_from = level, 
                values_from = c("contrastNominal","ratioContrastMeasuredNominal", "LMSBackgroundNominal")) %>%

    # Equate nominal contrast
    mutate(contrastNominal_high = contrastNominal_low) %>%
  
    # Pivot back to tall
    pivot_longer(cols = contains("_"),
                 names_to = c(".value", "level"),
                 names_pattern = "(.*)_(.*)"
                 )
```
Use the ratio of measured to nominal contrast to calculate `LMScontrastPredicted` from the `contrastNominal` of each acquisition.
```{r predict LMS contrast}
threshold_contrasts <- threshold_contrasts %>%
    # Predict LMS contrast from nominal predicted contrast
    mutate(LMScontrastPredicted = ratioContrastMeasuredNominal * contrastNominal)
```
Multiply by `LMSBackgroundNominal` to get `threshold_JND`.
```{r predict JNDs}
JNDs <- threshold_contrasts %>%
    # Calculate JND
    mutate(threshold_JND = LMScontrastPredicted * LMSBackgroundNominal)
```

# Plot the predicted JNDs in standard format
Normalize the JNDs by the median JND on the low melanopic background, calculate the `median_JNDs` per participant (after normalization), and plot.
```{r plot in standard format}
JNDs <- normalize_JNDs(JNDs)
plot_JNDs(JNDs) +
    ylab("Predicted threshold (LMS JND, normalized") +
    ggtitle("Predicted threshold, if flicker LMS splatter is considered")
```