---
title: "Effect of background LMS splatter on Adapt JNDs (Pulse1)"
---

Predicting JNDs as a function of the LMS content of the background spectra, under null-hypothesis that thresholds do not change.

Assume that nominal contrast at threshold on the high-melanopic pedestal is the same as nominal contrast on the low-melanopic background; what are the JNDs calculated from this nominal contrast and the measured LMS content of each background?
```{r setup}
library(tidyverse)
library(here)
source(here('R','clean_data.R'))
source(here('R','analyze_results.R'))
source(here('R','normalize_JNDs.R'))
source(here('R','results.plot.R'))
```
# Load in data
This dataset of thresholds in the Pulse1 experiment contains the columns:
`participant`,`session`,`axis`,`level`: meta info for each acquisition
`contrastNominal`: the nominal contrast at threshold
`LMSBackgroundNominal`: nominal LMS content of the background spectrum
`JNDNominal`: JND corresponding to the nominal contrast
`contrastMeasured`,`JNDMeasured`: measured contrast, JND, at threshold
`LMSBackgroundMeasured`: measured LMS content of the background spectrum
`JNDMeasured`: JND corresponding to the measured contrast and background
`ratioContrastMeasuredNominal`: ratio between nominal contrast, and measured contrast
`LMMeasured`: measured L-M contrast of the flicker on the background.
```{r load}
thresholds_splatter <- read_csv(here('data','experimental','pulse.thresholds.splatter.csv')) %>%
  mutate(JNDMeasured = JNDMeasuredQuick) %>%
  select(-JNDNominalFit, -JNDMeasuredQuick) %>%
  mutate(level = fct_relevel(level, "low","high"))  
```
# Cleaning
For the current analysis, need to group by the acquisition metadata, and need the nominal contrast (`contrastNominal`) and the measured LMS content of the background stimulus (`LMSBackgroundMeasured`). We also want to rename the participants.
```{r clean}
thresholds_splatter <- thresholds_splatter %>%
  rename_participants() %>%
  group_by(participant, session, axis, level)
```

# Visualize splatter
Visualize the measured LMS content of the background stimulus (`LMSBackgroundMeasured`), for separate participants, conditions, sessions.
```{r}
backgroundLMS <- thresholds_splatter %>%
  select(LMSBackgroundMeasured, LMSBackgroundNominal)
```
Normalize by expressing as proportion of nominal LMS content.
```{r normalize background LMS splatter}
backgroundLMS <- backgroundLMS %>%
  mutate(LMSBackgroundMeasured_Relative = LMSBackgroundMeasured / LMSBackgroundNominal)
```
## Plot the background LMS splatter
```{r visualize background LMS splatter}
ggplot(data = backgroundLMS) +
  # Setup mapping: melanopic level on horizontal, LMS content on vertical
  aes(x = level, y = LMSBackgroundMeasured_Relative) +
  # Separate panels for participants
  facet_grid(~ participant) +
  
  # Plot each session
  geom_line(aes(group = session), alpha = .6) +
  # Plot median for participant
  stat_summary(fun.y = median, geom = "point", aes(group=1), size =1) +
  stat_summary(fun.y = median, geom = "line", aes(group=1), size =1) +
  stat_summary(fun.y = median, fun.ymax = median_plus_sem, fun.ymin = median_minus_sem,
               geom = "linerange", aes(group = 1), size =1) +
  
  # Labeling
  geom_hline(yintercept = 1, linetype='solid') +
  ylab("Background LMS content (relative to nominal)") +
  xlab("Melanopic condition") +
  ggtitle("LMS splatter of backgrounds (Pulse1)") +
  theme_bw()
ggsave(here('figs','S4A.splatter.pulse.backgroundLMS.splatter.pdf'), width = 10, height = 5)
```
# Predict JNDs
Rotate dataframe to wide-format: separate columns for `high` and `low` nominal contrast at threshold per session. Set `high` nominal contrast at threshold equal to `low` nominal contrast at threshold. Rotate back to tall-format, with separate rows for low and high melanopic conditions indicated by columns `level` and `LMScontrastPredicted` for the predicted nominal contrast. Calculate `threshold_JND`, multiplying `LMScontrastPredicted` by `LMSBackgroundMeasured`.
```{r predict JNDs}
JNDs <- thresholds_splatter %>%
    # Convert to wide-format: separate columns for high/low
    select(contrastNominal) %>%
    spread(key = level, value = contrastNominal) %>%
    
    # Calculate contrast predicted:
    # Equate for contrast nominal
    mutate(high = low) %>%
    gather(low,high,key='level',value='LMScontrastPredicted') %>%
    mutate(level=factor(level,levels=c('low','high'))) %>%
    right_join(thresholds_splatter) %>%
    
    # Calculate JND
    mutate(threshold_JND = LMScontrastPredicted * LMSBackgroundMeasured)
```
## Plot the predicted JNDs in standard format
Normalize the JNDs by the median JND on the low melanopic background, calculate the `median_JNDs` per participant (after normalization), and plot.
```{r plot in standard format}
JNDs <- normalize_JNDs(JNDs)
plot_JNDs(JNDs) +
    ylab("Predicted threshold (LMS JND, normalized") +
    ggtitle("Predicted threshold, if background LMS splatter is considered (Pulse1)")
ggsave(here('figs','S4B.JNDs.pulse.backgroundLMS.splatter.pdf'), width = 10, height = 5)
```