---
title: "Effect of flicker LMS splatter on JNDs (Pulse1)"
---
```{r setup}
library(tidyverse)
library(here)
source(here('R','clean_data.R'))
source(here('R','analyze_results.R'))
source(here('R','normalize_JNDs.R'))
source(here('R','results.plot.R'))
```
# Load in data
This dataset of thresholds in the Pulse1 experiment contains the columns:
`participant`,`session`,`axis`,`level`: meta info for each acquisition
`contrastNominal`: the nominal contrast at threshold
`LMSBackgroundNominal`: nominal LMS content of the background spectrum
`JNDNominal`: JND corresponding to the nominal contrast
`contrastMeasured`,`JNDMeasured`: measured contrast, JND, at threshold
`LMSBackgroundMeasured`: measured LMS content of the background spectrum
`JNDMeasured`: JND corresponding to the measured contrast and background
`ratioContrastMeasuredNominal`: ratio between nominal contrast, and measured contrast
`LMMeasured`: measured L-M contrast of the flicker on the background.
```{r load}
thresholds_splatter <- read_csv(here('data','experimental','pulse.thresholds.splatter.csv')) %>%
  mutate(JNDMeasured = JNDMeasuredQuick) %>%
  select(-JNDNominalFit, -JNDMeasuredQuick) %>%
  mutate(level = fct_relevel(level, "low","high"))  
```
# Cleaning
For the current analysis, need to group by the acquisition metadata, and need the nominal LMS contrast (`contrastNominalQuick` and `contrastNominalFit`) and the measured LMS contrast of the flicker stimulus (`contrastMeasuredQuick`). Also need the `LMSBackgroundNominal` to convert to JNDs. We also want to rename the participants.
```{r clean}
thresholds_splatter <- thresholds_splatter %>%
  rename_participants() %>%
  group_by(participant, session, axis, level)
```
Calculate the ratio between the measured LMS content of the flicker stimulus at threshold (the `contrastMeasuredQuick`), and the nominal content of that stimulus (the `contrastNominalQuick`), for each acquisition.
```{r calculate ratio of measured to nominal flicker}
thresholds_splatter <- thresholds_splatter %>% 
    # Calculate ratio
    mutate(ratioContrastMeasuredNominal = contrastMeasured / contrastNominal)
```

# Plot the flicker LMS splatter
```{r visualize flicker LMS splatter}
ggplot(data = thresholds_splatter) +
  # Setup mapping: melanopic level on horizontal, LMS content on vertical
  aes(x = level, y = ratioContrastMeasuredNominal,
      group = participant) +

  # Plot median for each participant
  stat_summary(fun = median, geom = "point", size =1, alpha = .7, position=position_dodge(width = .08)) +
  stat_summary(fun = median, geom = "line", size =1,alpha = .7, position=position_dodge(width = .08)) +
  stat_summary(fun = median, fun.max = median_plus_sem, fun.min = median_minus_sem,
               geom = "linerange", size =1,alpha = .4, position=position_dodge(width = .08)) +  
  
  # Labeling
  geom_hline(yintercept = 1, linetype='solid') +
  ylab("Measured flicker LMS contrast") +
  xlab("Melanopic condition") +
  ggtitle("LMS splatter of flicker (Pulse 1)") +
  theme_bw()
ggsave(here('figs','5BL.splatter.pulse.flickerLMS.splatter.pdf'), width = 10, height = 5)
```
# Predict JNDs

```{r}
threshold_contrasts <- thresholds_splatter %>%
  select(contrastNominal, ratioContrastMeasuredNominal, LMSBackgroundNominal)
```
Pivot dataframe to wide-format: separate columns for `high` and `low` nominal contrast at threshold per session. Set `high` nominal contrast at threshold equal to `low` nominal contrast at threshold. Pivot back to tall-format, with separate rows for low and high melanopic conditions indicated by columns `level` and `contrastNominal` for the predicted nominal contrast.
```{r equate nominal contrasts}
threshold_contrasts <- threshold_contrasts %>%
    # Pivot to wide-format: separate columns for high/low
    pivot_wider(names_from = level, 
                values_from = c("contrastNominal","ratioContrastMeasuredNominal", "LMSBackgroundNominal")) %>%

    # Equate nominal contrast
    mutate(contrastNominal_high = contrastNominal_low) %>%
  
    # Pivot back to tall
    pivot_longer(cols = contains("_"),
                 names_to = c(".value", "level"),
                 names_pattern = "(.*)_(.*)"
                 )
```
Use the ratio of measured to nominal contrast to calculate `LMScontrastPredicted` from the `contrastNominal` of each acquisition.
```{r predict LMS contrast}
threshold_contrasts <- threshold_contrasts %>%
    # Predict LMS contrast from nominal predicted contrast
    mutate(LMScontrastPredicted = ratioContrastMeasuredNominal * contrastNominal)
```
Multiply by `LMSBackgroundNominal` to get `threshold_JND`.
```{r predict JNDs}
JNDs <- threshold_contrasts %>%
    # Calculate JND
    mutate(threshold_JND = LMScontrastPredicted * LMSBackgroundNominal)
```

# Plot the predicted JNDs in standard format
Normalize the JNDs by the median JND on the low melanopic background, calculate the `median_JNDs` per participant (after normalization), and plot.
```{r plot in standard format}
JNDs <- normalize_JNDs(JNDs)
ggplot(data = JNDs) +
    aes(x = level, y = JND, group=participant) +
    
    # Plot median for each participant
    stat_summary(fun = median, geom = "point", size =1, alpha = .6, color = "blue", position = position_dodge(width = .08)) +
    stat_summary(fun = median, geom = "line", size =1, alpha = .6, color = "blue", position = position_dodge(width = .08)) +
    stat_summary(fun = median, fun.max = median_plus_sem, fun.min = median_minus_sem,
                 geom = "linerange", size =1, alpha = .6, color = "blue", position = position_dodge(width = .08)) +
    
    # Markup
    scale_y_continuous(breaks = seq(-2,7,1), limits = c(-3,7)) +
    geom_hline(yintercept = 1, linetype='solid') +
    geom_hline(yintercept = 4.5, linetype='dashed') +    
    ylab("Predicted threshold (LMS JND, normalized") +
    xlab("Adaptation level") +
    theme_bw() +
    ggtitle("Predicted threshold, if flicker LMS splatter is considered")
ggsave(here('figs','5BR.JNDs.pulse.flickerLMS.splatter.pdf'), width = 10, height = 5)
```