---
title: "Effect of flicker L-M splatter on JNDs (Pulse1)"
---
```{r setup}
library(tidyverse)
library(here)
source(here('R','clean_data.R'))
source(here('R','analyze_results.R'))
source(here('R','normalize_JNDs.R'))
source(here('R','results.plot.R'))
```
# Load in data
This dataset of thresholds in the Pulse1 experiment contains the columns:
`participant`,`session`,`axis`,`level`: meta info for each acquisition
`contrastNominal`: the nominal contrast at threshold
`LMSBackgroundNominal`: nominal LMS content of the background spectrum
`JNDNominal`: JND corresponding to the nominal contrast
`contrastMeasured`,`JNDMeasured`: measured contrast, JND, at threshold
`LMSBackgroundMeasured`: measured LMS content of the background spectrum
`JNDMeasured`: JND corresponding to the measured contrast and background
`ratioContrastMeasuredNominal`: ratio between nominal contrast, and measured contrast
`LMMeasured`: measured L-M contrast of the flicker on the background.
```{r load}
thresholds_splatter <- read_csv(here('data','experimental','pulse.thresholds.splatter.csv')) %>%
  mutate(JNDMeasured = JNDMeasuredQuick) %>%
  select(-JNDNominalFit, -JNDMeasuredQuick) %>%
  mutate(level = fct_relevel(level, "low","high"))  
```
# Cleaning
For the current analysis, need to group by the acquisition metadata, and need the nominal LMS contrast (`contrastNominal`) and the measured L-M contrast of the flicker stimulus at nominal threshold LMS contrast (`LMMeasured`). Also need the `LMSBackgroundNominal` to convert to JNDs. We also want to rename the participants.
```{r clean}
thresholds_splatter <- thresholds_splatter %>%
  rename_participants() %>%
  group_by(participant, session, axis, level)
```
```{r calculate L-M/(L+M+S)}
thresholds_splatter <- thresholds_splatter %>%
  mutate(LMoverLMSmeasured = LMMeasured/contrastMeasured,
         LMoverLMSnominal = LMMeasured/contrastNominal)
```
# Plot the flicker L-M splatter
`LMMeasured`: measured L-M contrast of the flicker on the background, at nominal threshold LMS contrast.
```{r visualize flicker LMS splatter}
ggplot(data = thresholds_splatter) +
  # Setup mapping: melanopic level on horizontal, L-M contrast on vertical
  aes(x = level, y = LMoverLMSmeasured) +
  # Separate panels for participants
  facet_grid(~ participant) +
  
  # Plot each session
  geom_line(aes(group = session), alpha = .6) +
  # Plot median for participant
  stat_summary(fun.y = median, geom = "point", aes(group=1), size =1) +
  stat_summary(fun.y = median, geom = "line", aes(group=1), size =1) +
  stat_summary(fun.y = median, fun.ymax = median_plus_sem, fun.ymin = median_minus_sem,
               geom = "linerange", aes(group = 1), size =1) +  
  
  # Labeling
  geom_hline(yintercept = 0, linetype='solid') +
  ylab("Measured flicker (L-M)/(L+M+S) contrast") +
  xlab("Melanopic condition") +
  ggtitle("L-M splatter of flicker at thresholds") +
  theme_bw()
ggsave(here('figs','S6A.splatter.pulse.flickerLM.splatter.pdf'), width = 10, height = 5)
```
# Predict JNDs
If L-M contrast detection is the mechanism setting thresholds in the current experiment, what would the predcited JNDs be? Assume (absolute) `LMMeasured` at threshold is constant across melanopic conditions. (absolute) `LMMeasured` related to nominal LMS contrast by `LMoverLMsnominal`, so predict nominal LMS contrast at threshold from that. Multiply predicted LMS contrast by background LMS content to predict JND.
```{r calculate abs(L-M)/(L+M+S)}
threshold_contrasts <- thresholds_splatter %>%
  mutate(LMMeasured = abs(LMMeasured),
         LMoverLMSmeasured = LMMeasured/contrastMeasured,
         LMoverLMSnominal = LMMeasured/contrastNominal) %>%
  select(LMMeasured, LMoverLMSnominal, LMSBackgroundNominal)
```
Pivot dataframe to wide-format: separate columns for `high` and `low` conditions, row per session. Set L-M contrast at threshold in `high` condition equal to L-M contrast at threshold in in `low` condition. Pivot back to tall-format, with separate rows for low and high melanopic conditions indicated by column `level`.
```{r equate nominal contrasts}
threshold_contrasts <- threshold_contrasts %>%
    # Pivot to wide-format: separate columns for high/low conditions, each row is a session
    pivot_wider(names_from = level, 
                values_from = c("LMMeasured","LMoverLMSnominal", "LMSBackgroundNominal")) %>%

    # Equate nominal contrast
    mutate(LMMeasured_high = LMMeasured_low) %>%
  
    # Pivot back to tall
    pivot_longer(cols = contains("_"),
                 names_to = c(".value", "level"),
                 names_pattern = "(.*)_(.*)"
                 )
```
Use the ratio of measured L-M to nominal contrast to calculate `LMScontrastPredicted` from the `LMMeasured` of each acquisition.
```{r predict LMS contrast}
threshold_contrasts <- threshold_contrasts %>%
    # Predict LMS contrast from nominal predicted contrast
    mutate(LMScontrastPredicted = LMMeasured / LMoverLMSnominal)
```
Multiply by `LMSBackgroundNominal` to get `threshold_JND`.
```{r predict JNDs}
JNDs <- threshold_contrasts %>%
    # Calculate JND
    mutate(threshold_JND = LMScontrastPredicted * LMSBackgroundNominal)
```

# Plot the predicted JNDs in standard format
Normalize the JNDs by the median JND on the low melanopic background, calculate the `median_JNDs` per participant (after normalization), and plot.
```{r plot in standard format}
JNDs <- normalize_JNDs(JNDs)
plot_JNDs(JNDs) +
    ylab("Predicted threshold (LMS JND, normalized") +
    ggtitle("Predicted threshold, if flicker LMS splatter is considered")
ggsave(here('figs','S6B.JNDs.pulse.flickerLM.splatter.pdf'), width = 10, height = 5)
```